mixchar

### 2018-08-13 manuscript/manuscript.Rnw
revise operating system and CRAN notes

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}
The package can work with either Windows, Mac OS X, or Linux.

@@

{\bf Archive} (e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] The name of the archive.
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Publisher:] Name of the person who deposited the software.
	\item[Version published:] The version number of the software archived.
	\item[Date published:] dd/mm/yy
\end{description}

{\bf Code repository} GitHub

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \url{https://github.com/smwindecker/mixchar/}
	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 https://doi.org/10.5281/zenodo.1343849
	\item[Licence:] MIT and open license as found on https://github.com/smwindecker/mixchar/releases/tag/v0.1.0.
	\item[Date published:] 11/08/2018
\end{description}

>>>>

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}
The package was tested on Windows, Mac OS X, and Linux.

@@

{\bf Archive}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] CRAN
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Publisher:] Name of the person who deposited the software.
	\item[Version published:] 0.1.0
	\item[Date published:] dd/mm/yy
\end{description}

{\bf Code repository}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] Github \url{https://github.com/smwindecker/mixchar/}
	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 https://doi.org/10.5281/zenodo.1343849
	\item[Licence:] MIT and open license as found on https://github.com/smwindecker/mixchar/releases/tag/v0.1.0.
	\item[Date published:] 11/08/2018
\end{description}
